WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-05 paper/reviews_ds.Rmd
rewrite 7b

We agree that it is important to make open data findable beyond just providing it freely.
Digital object identifiers are the de-factor standard for making unique references to data sets. In line with the reviewer's suggestion,
we suggest to use external providers to provide such DOIs while github is still the primary data storage. TODO!!!

Our prefered route is to use github web hooks to link Zenodo and a WORCS-compatible repository. With this technique, Zenodo issues DOI for content hosted on github repositories including some nice extras, such as automatic badge DOI badges for the repository.

BV: Can you please argue for why GitHub is equivalent to Zenodo for this purpose?
AL: Can you address the reference to FAIR principles in relation to GitHub?
CJ: I will address "big" data

on second thought, it’s probably worth mentioning to the reviewer that we know these options but defend the OSF-centric approach for our purposes. My impression is that the main challenge are the different expectations and solutions across disciplines that are currently evolving largely in parallel. If we acknowledge that there are alternatives, this may please the reviewers while we still can defend R + OSF for the behavioral and social sciences. Other disciplines may have different foci, e.g., python + jupyter + docker etc... and no single manuscript will be able to cover everything.

>>>>

A crucial advantage of storing the data on GitHub, relative to Zenodo or FigShare,
is that they are bundled with the
documentation (e.g., codebook), analysis code, and manuscript.
Thus, readers have access to **all** materials required for replication in one repository.
GitHub additionally offers user interaction with the materials through
forking, cloning, opening issues, and sending pull requests -
all useful tools for replication and collaboration.

We agree that it is important to make open data findable beyond just providing it freely.

The approach we advocate is to make all of a project's resources available in a 
Step 15 of the workflow, "Connect your ‘OSF’ project page to the ‘Git’ remote repository",
was intended to meet this goal.
However, we acknowledge that this requires further clarification.

Particularly the addition of a robust citation for the data is an essential step that should have been mentioned in the manuscript.
In the revision, we have addressed this by adding a step to the WORCS workflow, and discussing DOIs in the paper.

Unfortunately, the Reviewer preference for Zenodo or FigShare is not explained.
We consider these platforms to be somewhat interchangeable with using Git remote repositories - with one key distinction:

Digital object identifiers are the de-factor standard for making unique references to data sets. In line with the reviewer's suggestion,
we suggest to use external providers to provide such DOIs while github is still the primary data storage. TODO!!!

BV: Can you please argue for why GitHub is equivalent to Zenodo for this purpose?
AL: Can you address the reference to FAIR principles in relation to GitHub?

AB: "on second thought, it’s probably worth mentioning to the reviewer that we know these options but defend the OSF-centric approach for our purposes. My impression is that the main challenge are the different expectations and solutions across disciplines that are currently evolving largely in parallel. If we acknowledge that there are alternatives, this may please the reviewers while we still can defend R + OSF for the behavioral and social sciences. Other disciplines may have different foci, e.g., python + jupyter + docker etc... and no single manuscript will be able to cover everything."
